Estimating Neighborhood Rents with Scraped Data

### 2018-06-03 index.rmd
adding <br> to after objective on main index
typo in index, reducing footer whitespace

The goal of this research is to understand the spatial and temporal dynamics of rent estimates in Seattle using scraped rental housing listings from Craigslist. I use a series of data visualizations to describe the overall datam, after which I model a panel of quarterly census tract estimates to explain the dynamics observed so far and forecast a surface of rent values for the current quarter.

@@

[Working paper on estimating Seattle neighborhood rent indicators](./manuscript/index.html)

>>>>

The goal of this research is to understand the spatial and temporal dynamics of rent estimates in Seattle using scraped rental housing listings from Craigslist. I use a series of data visualizations to describe the overall data, after which I model a panel of quarterly census tract estimates to explain the dynamics observed so far and forecast a surface of rent values for the current quarter.

@@

[Working paper](./manuscript/index.html) on estimating Seattle neighborhood rent indicators
